LAGOS lake depth

### 2021-08-16 tables/02_model_metrics.Rmd
render more complex table 1(2), closes #27

dt_metrics <- tidy_grid_metrics(
  readRDS("../data/01_depth_model/depth_grid_metrics.rds")[[1]])

>>>>

dt_raw <- readRDS("../data/01_depth_model/depth_grid_metrics.rds")
dt_metrics <- lapply(dt_raw, tidy_grid_metrics)
dt_metrics <- do.call("rbind", dt_metrics)
dt_metrics$filter <- ""
dt_metrics$filter[c(1, 5, 9, 13, 17)] <- c("all", "reservoir", "natural lake", "convex", "concave")
# dt_metrics$filter <- c(rep("all", 4), rep("reservoir", 4),
#   rep("natural lake", 4), rep("convex", 4), rep("concave", 4))
dt_metrics <- dplyr::relocate(dt_metrics, filter)
